Computable Poincar\'e--Friedrichs constants for the $L^{p}$ de Rham complex over convex domains and domains with shellable triangulations

### 2024-10-03 main.tex
progress on reflection mapping

        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in a face $F$ of $T$. 
        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of $F$ in $T$. 
        Thus 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            \leq 
            (n-k) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-k }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We abbreviate 
        \begin{align*}
            B_{T} 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align*}

        \item 
        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Phi$.
        We construct a bi-Lipschitz mapping 
        \begin{align*}
            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}
        \end{align*}
        and analyze its properties. The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
        will define the required mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
        which will be bi-Lipschitz and the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.

        We write $h_{z}$ for the height of $z_{S'}$ within $K$.
        Given $x \in K \cup K^{c}$, we have a unique representation
        \begin{align*}
            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c}.
        \end{align*}
        Notice that 
        \begin{align*}
            t = \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{K}(x) := x - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.

>>>>

        Recall that $K \in \calR$ is obtained from $T$ via barycentric subdivisions, first at $z_{S}$ and then at $z_{S'}$. 
        Let $F_{z} \subseteq K$ be the face opposite to the vertex $z_{S'}$,
        which must be contained in some face of $T$. 
        Since $S'$ has dimension $n-k-1$, the vector $(n-k) h_{z}$ is the height vector of that face of $T$. 
        Thus 
        \begin{align*}
            \frac{ \vecnorm{ b_{z} } }{ \vecnorm{ h_{z} } }
            = 
            \frac{ \vecnorm{ b_{z} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            = 
            \frac{ \vecnorm{ z_{S'} } }{ (n-k)^{-1} \| (n-k) h_{z} \| }
            \leq 
            (n-k) \aspectratio(T)
%             = 
%             \frac{ \vecnorm{ b_{z} } \vol(F_{z}) }{ (n-k)^{-1} n \vol(T) }
%             \leq 
%             \frac{ n-k }{n!}
%             \cdot 
%             \frac{ \diam(T)^{n} }{ \vol(T) }
            .
        \end{align*}
        This establishes bounds on the singular values of the transformation. 
        We abbreviate 
        \begin{align*}
            B_{T} 
            := 
%             \sqrt{ 1 + \tan^{2}(\beta) } - \tan(\beta) 
%             \geq 
            \sqrt{ 
                1 + (n-k)^{2} \aspectratio(T)^{2} % \frac{ \diam(T)^{2n} }{ n!^{2}\vol(T)^{2} } 
            } 
            + 
            (n-k) \aspectratio(T) % \frac{ \diam(T)^{n} }{ n! \vol(T) }            
            .
        \end{align*}

        \item 
        We introduce another mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$ as follows. 
        Consider any $n$-simplex $K \in \calR$ and let $K^c \in \calR^{c}$ be its image under $\Theta$.
        We construct a bi-Lipschitz mapping 
        \begin{align*}
            \Phi_{K} : K \cup K^{c} \rightarrow K^{c}.
        \end{align*}
        The construction will be such that the union of $\Phi_{K}$ for all $n$-simplices $K \in \calR$
        will define the desired bi-Lipschitz mapping $\Phi : \underlying{\calR'} \rightarrow \underlying{\calR^{c}}$,
        which will be the identity along $\partial\underlying{\calR'} \setminus \partial\underlying{\calR}$.

        Once again, $h_{z}$ denotes the height of $z_{S'}$ within $K$.
        Any $x \in K \cup K^{c}$ has a unique representation
        \begin{align*}
            x = t z_{S} + x^{\perp}, \quad t \in [-1,1], \quad x^{\perp} \in K \cap K^{c},
        \end{align*}
        where we have 
        \begin{align*}
            t = t(x) := \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} 
            .
        \end{align*}
        Based on that observation, we define 
        \begin{align*}
            \Phi_{K}(x) 
			:= 
			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x^{\perp} - \frac 1 2 \left( \frac{\langle h_{z},x\rangle}{\langle h_{z},z_{S'}\rangle} - 1 \right) z_{S'}
            .
        \end{align*}
        We can write 
        \begin{align*}
            \Phi_{K}(x) 
			:= 
			x^{\perp} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x^{\perp} + t(x) z_{S'} - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x - t(x) z_{S'} - \frac 1 2 \left( t(x) - 1 \right) z_{S'}
            = 
			x - t(x) z_{S'} - \frac 1 2 \left( 3 t(x) - 1 \right) z_{S'}
            .
        \end{align*}
        We readily verify that this transformation is a bi-Lipschitz mapping from $K \cup K^{c}$ onto $K^{c}$
        that satisfies the desired mapping properties. 
        It remains to analyze its Jacobian to get explicit estimates.
